---
title: "IsoChrone Trials"
author: "Orhan Aktas"
date: '2022-08-16'
output:   
    html_document:
      df_print: !expr knitr::kable
      toc: yes
      number_sections: yes
      toc_depth: 2
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  class.source = "bg-warning text-warning"
)
```

#### Required Libraries {.unlisted .unnumbered}

```{r libraries, message=FALSE, warning=FALSE}
library(osrm)
library(sf)
library(tidyverse)
library(leaflet)
```

# Introduction

This root code is taken from this [link](https://gis.stackexchange.com/questions/347807/using-osrm-to-create-isochrones-in-r-potentially-problematic-at-10-minutes-dri).

## create locations data

first I want to add only one station.

```{r}
locations <- tibble::tribble(
  ~place,       ~lon,     ~lat,
  "Erenköy", 29.076372484549257, 40.971632584204116)
```

then I will add the second and work on scaling. Here is the second stations data.

`"Göztepe",29.065281554810728,40.97964287391979`

## Create isochrones

isochrones can be created for drive (default), bike and walk.

### isochrones for walking

only for two isochrones. 5 min and 10 min. In this map, there is a problem with the areas. There are some holes in them.

```{r}
iso <- osrmIsochrone(loc = c(locations$lon, locations$lat), 
                     breaks = seq(from = 0,to = 10, by = 5),
                     res=40,
                     osrm.profile="foot")

iso$drive_times <- factor(paste(iso$min, "to", iso$max, "min"))

factpal <- colorFactor("RdYlBu", iso$drive_times)

leaflet() %>%
  setView(mean(locations$lon), mean(locations$lat), zoom = 7) %>% 
  addMarkers(lng = locations$lon, lat=locations$lat) %>% 
  addProviderTiles("CartoDB.Positron", group="Greyscale") %>% 
  addPolygons(fill=TRUE, stroke=TRUE, color = "black",
              fillColor = ~factpal(iso$drive_times),
              weight=0.5, fillOpacity=0.2,
              data = iso, popup = iso$drive_times,
              group = "Drive Time") %>%
  addLegend("bottomright", pal = factpal, values = iso$drive_time,   title = "Drive Time")
```

And this is for four isochrones.

```{r}
iso <- osrmIsochrone(loc = c(locations$lon, locations$lat), 
                     breaks = seq(from = 0,to = 20, by = 5),
                     res=40,
                     osrm.profile="foot")

iso$drive_times <- factor(paste(iso$min, "to", iso$max, "min"))

factpal <- colorFactor("RdYlBu", iso$drive_times)

leaflet() %>%
  setView(mean(locations$lon), mean(locations$lat), zoom = 7) %>% 
  addMarkers(lng = locations$lon, lat=locations$lat) %>% 
  addProviderTiles("CartoDB.Positron", group="Greyscale") %>% 
  addPolygons(fill=TRUE, stroke=TRUE, color = "black",
              fillColor = ~factpal(iso$drive_times),
              weight=0.5, fillOpacity=0.2,
              data = iso, popup = iso$drive_times,
              group = "Drive Time") %>%
  addLegend("bottomright", pal = factpal, values = iso$drive_time,   title = "Drive Time")
```

### isochrones for cycling

only for two isochrones. 5 min and 10 min.

```{r}
iso <- osrmIsochrone(loc = c(locations$lon, locations$lat), 
                     breaks = seq(from = 0,to = 10, by = 5),
                     res=40,
                     osrm.profile="bike")

iso$drive_times <- factor(paste(iso$min, "to", iso$max, "min"))

factpal <- colorFactor("RdYlBu", iso$drive_times)

leaflet() %>%
  setView(mean(locations$lon), mean(locations$lat), zoom = 7) %>% 
  addMarkers(lng = locations$lon, lat=locations$lat) %>% 
  addProviderTiles("CartoDB.Positron", group="Greyscale") %>% 
  addPolygons(fill=TRUE, stroke=TRUE, color = "black",
              fillColor = ~factpal(iso$drive_times),
              weight=0.5, fillOpacity=0.2,
              data = iso, popup = iso$drive_times,
              group = "Drive Time") %>%
  addLegend("bottomright", pal = factpal, values = iso$drive_time,   title = "Drive Time")
```

### isochrones for driving

only for two isochrones. 5 min and 10 min. There is a problem with the location data in this map.

```{r}
iso <- osrmIsochrone(loc = c(locations$lon, locations$lat), 
                     breaks = seq(from = 0,to = 10, by = 5),
                     res=40)

iso$drive_times <- factor(paste(iso$min, "to", iso$max, "min"))

factpal <- colorFactor("RdYlBu", iso$drive_times)

leaflet() %>%
  setView(mean(locations$lon), mean(locations$lat), zoom = 7) %>% 
  addMarkers(lng = locations$lon, lat=locations$lat) %>% 
  addProviderTiles("CartoDB.Positron", group="Greyscale") %>% 
  addPolygons(fill=TRUE, stroke=TRUE, color = "black",
              fillColor = ~factpal(iso$drive_times),
              weight=0.5, fillOpacity=0.2,
              data = iso, popup = iso$drive_times,
              group = "Drive Time") %>%
  addLegend("bottomright", pal = factpal, values = iso$drive_time,   title = "Drive Time")
```
